How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-27 Manuscript.tex
Updates from ShareLaTeX

\title{How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{4} 
\author{  
\alignauthor
Rahul~Krishna\\Tim Menzies, Xipeng~Shen \\
       \affaddr{CS, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Andrian Marcus \\
       \affaddr{CS, UT Dallas  } \\ 
       \affaddr{Texas, USA}\\ 
       {amarcus@utdallas.edu}
       \alignauthor
Naveen  \\ Lekkalapudi\\
 \affaddr{Bellhops } \\ 
       \affaddr{Tennessee, USA}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 Business users now demand more insightful
 analytics. Instead of just predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  what to change  in order to
 improve on the predicted values.

 This paper proposes
 and evaluates the  XTREE planner for software projects. 
XTREE inputs tables of data with independent features plus a   weighted class
that indicate how much each row is  ``bad'' or  ``better''. Plans are edits proposed for each 
row such that the changed row is more likely to be ``better''.  XTREE
learns those plans by building a decision tree across the data, then reporting
the differences in the branches from some current branch to another desired branch.

@@

The contributions of this paper are (1)  
    the new XTREE    algorithm and (2) an evaluation strategy for   planners.
In the case studies of this paper  our evaluations shows
 XTREE performing significantly ``better'' than    planners  proposed in our prior   work~\cite{me12c,krishna15},
 where ``better'' means 
{\em effective} (plans change the  expected values of the class);
{\em succinct} (it is inconvenient if  plans   always require changing  everything);
and {\em surprising} (a planner should sometimes tell us things we do not expect
since, otherwise,
there is no value added from  using the planner).

The rest of this paper   describes our data, our planners, and the experiment that
ranks XTREE against alternate approaches.  This is followed by notes on related work
and validity.
Note that, to allow for reproducibility, all scripts and data used in this 
study are available on-line at github.com/ai-se/XTREE.

@@

Our planners   use tables of data with independent features and one dependent feature, called the 
``class''. Classes are weighted such that they indicate  what rows are ``bad'' and what rows are ``better''. Plans  change   a row such that it is more likely to be ``better''. 
Specifically, for every test example $Z$,   planners proposes a  plan $\Delta$ to
  adjust   feature $Z_j$:
\[
\forall \delta_j \in \Delta :  Z_j = Z_j + \delta_j
\]
For example, to simplify a  large bug-prone  method, our planners might suggest
to a developer to reduce its size (i.e.  refactor that code by, say, splitting it across
two simpler functions).

@@

To answer this question, we note
that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
(for a visualization of these clouds, see \fig{howxy}).
\begin{figure}[!t]
  \includegraphics[width=.9\linewidth]{figs/twodee.eps} 
 % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
\caption{Gray, red, green show (1) training examples, (2) test examples and 
  (3) tests that have been altered by planners.
  This figure uses axes generated from the first two components of a PCA analysis of all points. 
}\label{fig:howxy}
\end{figure}
We should mistrust the predictions made by a  model   if it is being applied to examples  that are
too far away from the
training cloud.
To test for ``too far'', we can run a data mining experiment that tests how well
a model learned from the training data applies to the test data. Such experiments return some performance value.

@@

That said, the above comes with some important caveats:
\bi
\item 
We   strongly recommend that predictors are assessed prior to planning. That
issue is explored further in the \tion{tesd}.
\item
Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
\item
Where possible, planners should be assessed via some external
oracle that can accurately assess new examples. For an example of that kind of analysis,
see  \tion{coc}.
\ei

@@

   The Jurecko data records number of known defects for each class, where the classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc. For details on the Jurecko data, see  \fig{ck} and \fig{jd}. 
 For the most part, the methods of this paper treat
  the Jurecko as a discrete class data set, where {\em defects} are true if the raw defect count is greater than zero.
  The one exception will be the `best-in-cluster'' method that reflects on the numeric value of the raw defect count (see \tion{BIC}).

@@

As a preliminary study, we split the Jureczko  data   into equal sized train:test groups.
Random Forests (again, from the SciKit learn kit~\cite{Pedregosa2012}) were
built from the training data, then applied to the test data.
The ``untuned'' columns of \fig{j} shows those results.
If we define ``good'' to mean $\mathit{pd}>60 \wedge \mathit{pf} < 40$\%,
then only two of our data sets ({\em ivy,ant}) are ``good'' enough for this study.
Note that, as might have been expected, none of the \colorbox{lavenderpink}{three bottom rows} of \fig{j} were ``good''.

Fortunately,
the ``tuned'' columns of \fig{j} show that we can salvage some of the data sets. Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples. Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
for tree generation, etc. The rows \colorbox{celadon}{marked with a $\star$} in \fig{j} show data sets whose performance was improved remarkably by these techniques. For example, in {\em poi}, the recall increased by 4\% while the false alarm rate dropped by 21\%. However,  as might have been expected, we could not salvage the data sets in the  three bottom rows.

@@

\newpage \section{Experiments}

@@

 \begin{figure}[!h]
{\small 
\[
\begin{array}{r} 
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; XTREE)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{before}& =\mathrm{Performance\; scores \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{before} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} R=\frac{\mathit{after}}{\mathit{before}}
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]}
 \caption{Experimental .}\label{fig:design}
 \end{figure}

@@

@@

 As to the method that lead to best effectiveness in \fig{jur} and \fig{conf1}, we note from \fig{types}
 that XTREE
 has a consistent behavior in both the discrete and continuous data sets.  Specifically,  in all our data sets,
 XTREE changes 
 usually changes around a fifth of the features.

@@

Such a surprising plan can be  seen in the {\em lucene} results. Recall the standard advice for
OO systems: build classes that are internally cohesive with low coupling to other parts of the system~\cite{Dhama199565}. We can assess the relevance of this advice
to specific projects by checking how often a planner changes the
 coupling-related features:
\bi
\item {\em ca}:   afferent couplings  =  how many other classes use the specific
				class;
\item {\em  	ce}:  efferent couplings =  how many other classes is used by the
				specific class. 
\item {\em cbm}: coupling between methods =  total number of new/redefined methods
				to which all the inherited methods are coupled
\item	{\em cbo}:  coupling between objects = a value that increases when the methods of one
				class access services of another.

\item {\em ic}:   inheritance coupling =  number of parent classes to which a given
				class is coupled (includes counts of methods and variables inherited)
\ei
For the  {\em lucene} XTREE results  of  \fig{changed},
the most frequent change was to alter the lines of code in a class (see the tallest
red historgram in that figure on the {\em loc}, or lines of code). 
Looking at the logs of our planner, we can see
that XTREE's proposed changed is to {\em reduce} the size of a class.
The only way to do that,  while keeping the  same functionality, it is create a network
of smaller classes that interact to produce that functionality.
That is, we would need to {\em increase} the coupling of those classes to achieve XTREE's plan.

@@

In summary, XTREE satisfies that criteria that, sometimes, it produces surprising plans.
At least for the {\em lucense} data set, we can see advice that recommends {\em increasing coupling}
to reduce defects.

@@

For example, the COCOMO model from University of 
Southern California estimates software development time using a combination of industrial data and some domain expertise
from its author (Barry Boehm). \fig{coc} shows results from using COCOMO 
as an oracle to assess our planning methods. In this experiment, random projects were used as COCOMO
inputs. This generated an development time estimate for each example, which we passed to our four methods.
40 times, we let those methods propose changes to those projects. 
For assessment purposes, the changes projects were then feed back to the COCOMO
oracle.

Using this approach, it is possible to assess the value of a plan by measuring its
effectiveness with respect to some ground truth (in this case, the COCOMO model).
As shown in \fig{coc}, XTREE passes this assessment.
Those results from the COCOMO model endorsed the conclusions of the rest
of this paper; i.e. compared to three other methods,  XTREE's supervised methods are best for generating plans on how to change
example projects.

\subsection{  Feasibility}\label{sect:feasibility}
It is important to also explore the general practicality of the plans. To this end, we are currently undertaking is a \textit{feasibility study} collaboration with industrial partners to assess the general feasibility of our changes. With this study, we would like to understand the nature of changes suggested by XTREE. Specifically: are the changes proposed by XTREE small enough to be easily implemented on software projects? Also, are the changes large enough to be feasible? In other words, we are asking if users can sufficient fine-grained control to make the changes proposed in \fig{changed}.

@@

Some organizations have the resources to 
run repeated trials to assess  different treatments.
For example, in one remarkable recent study, Bente et al. report results
were the same for specification that was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
to (say) take a code base, assign it to different teams, make these teams  adopt different polices,
then check in 12 months time
 which teams have fewer defects than the others.

@@

Four planners were assessed here for the tasks of reducing defects and runtimes. 
Three of the methods come from our prior publications~\cite{me12c,krishna15}, and the conclusion of this
paper is that a novel fourth method clearly out-performs the other three
(measured in terms of {\em effectiveness, succinctness, and surprise}).
We conjecture that XTREE worked better than the rest since:
\bi
\item
It uses a supervised method to divide the data and;
\item
When planning how to move examples to better classes, it is   best to use a learner that reflects over 
differences between the classes.
\ei

@@

As to scalability, XTREE is a post-processor to a decision tree algorithm. Hence, in theory,  XTREE should work on
any domain where data miners can generate decision trees. Given the current state of the art in Big Data,
can   XTREE  be applied to  very large data sets?

@@

\section*{Acknowledgements}
The work has partially funded by a National Science Foundation CISE CCF award \#1506586.
\bibliographystyle{plain}

>>>>

\title{How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{4} 
\author{  
\alignauthor
Rahul~Krishna\\Tim Menzies, Xipeng~Shen \\
       \affaddr{CS, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Andrian Marcus \\
       \affaddr{CS, UT Dallas  } \\ 
       \affaddr{Texas, USA}\\ 
       {amarcus@utdallas.edu}
       \alignauthor
Naveen  \\ Lekkalapudi\\
 \affaddr{Bellhops } \\ 
       \affaddr{Tennessee, USA}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 Business users now demand more insightful
 analytics; specifically, tools that generate ``plans''--
  specific suggestions on  what to change  in order to
 improve  the predicted values.

 This paper proposes  the  XTREE planner for software projects. 
XTREE inputs tables of data of independent features plus a   weighted class
  indicating how much each row is  ``bad'' or  ``better''. 
  Plans are edits to  
rows such that the changed row is more likely to be ``better''.  XTREE
learns those plans by building a decision tree across the data, then reporting
the differences in the branches from some current branch to another desired branch.

@@

The contributions of this paper are (1)  
    the new XTREE    algorithm and (2) an evaluation strategy that shows
 XTREE performing significantly ``better'' than    planners  proposed in our prior   work~\cite{me12c,krishna15},
 where ``better'' means 
{\em effective} (plans change the  expected values of the class);
{\em succinct} (it is inconvenient if  plans   always require changing  everything);
and {\em surprising} (a planner should sometimes tell us things we do not expect
since, otherwise,
there is no value added from  using the planner).

The rest of this paper   describes our data, our planners, and the experiment that
ranks XTREE against alternate approaches.  This is followed by notes on related work
and validity.
To enable reproducibility, all scripts and data used in this 
study are available on-line at github.com/ai-se/XTREE.

@@

Our planners   use tables of data with independent features and a dependent class
feature. Classes have weights  that  indicate  what rows are ``bad'' or ``better''. Plans  change   a row such that it is more likely to be ``better''. 
Specifically, for every test example $Z$,   planners proposes a  plan $\Delta$ to
  adjust   feature $Z_j$:

{\small\[
\forall \delta_j \in \Delta :  Z_j =  
\begin{cases}
     Z_j + \delta_j& \text{if $Z_j$ is numeric}\\
    \delta_j              & \text{otherwise}
\end{cases}
\]}
For example, to simplify a  large bug-prone  method, our planners might suggest
to a developer to reduce its size (i.e.  refactor that code by, say, splitting it across
two simpler functions).

@@

To answer this question, we note
that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
(for a visualization of these clouds, see \fig{howxy}).
\begin{figure}[!t]
  \includegraphics[width=\linewidth]{figs/twodee.eps} 
 % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
\caption{Gray, red, green show (1) training examples, (2) test examples and 
  (3) tests that have been altered by planners.
  This figure uses axes generated from the first two components of a PCA analysis of all points. 
}\label{fig:howxy}
\end{figure}
We should mistrust the predictions made by a  model   if it is being applied to examples  that are
too far away from the
training cloud.
To test for ``too far'', we can run a data mining experiment that tests how well
a model learned from the training data applies to the test data. Such experiments return some performance value.

@@

That said, the above comes with some important caveats:
\bi
\item 
The quality of the prediction depends on the nature of the training data. Thus, we strongly recommend that both data set and the predictor be assessed prior to planning. This ensures that the predictor's performance is adequate for a data set. We tackle this issue in detail in \tion{tesd}.
\item
Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
\item
Where possible, planners should be assessed via some external
oracle that can accurately assess new examples. For an example of that kind of analysis,
see  \tion{coc}.
\ei

@@

   The Jurecko data records number of known defects for each class using a post-release bug tracking system. The classes are described in terms of
  nearly two dozen metrics such as number of children, lines of code, etc. For details on the Jurecko data, see  \fig{ck} and \fig{jd}. 
 All the planning methods of this paper reflect on the numeric value of the raw defect counts. The predictor considers defects to be a discrete class data set,where defects are \textit{\texttt{TRUE}} if the numeric defect count is greater than zero and \textit{\texttt{FALSE}} otherwise.

@@

As a preliminary study, we split the Jureczko  data into train and test groups.
Random Forests (again, from the SciKit learn kit~\cite{Pedregosa2012}) were
built from the training data, then applied to the test data.
The ``untuned'' columns of \fig{j} shows those results. We called a data set ``usable'' if Random Forest was able to classify majority of the instances correctly. For this purpose, we set a threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% to select these data sets. With this threshold, however, none of our data sets were be suitable for this study.

Fortunately, the ``tuned'' columns of \fig{j} show that we can salvage some of the data sets. Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples and under-sampling of majority-class examples. Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
for tree generation, etc. The rows \colorbox{celadon}{marked with a $\star$} in \fig{j} show data sets whose performance was improved remarkably by these techniques. For example, in {\em poi}, the recall increased by 4\% while the false alarm rate dropped by 21\%. However,  as might have been expected, we could not salvage the data sets in the  three bottom rows.

@@

\section{Experiments}

@@

 \begin{figure}[!h]
{\small 
\[
\begin{array}{r} 
\mathrm{project}\\
\mathrm{data}
\end{array} 
\left\{\begin{array}{l}\mathit{train}
        \left\{\begin{array}{l}
                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; XTREE)}
              \end{array}\right.
       \\
      ~\\
\mathit{test}  
    \left\{\begin{array}{l@{~}l}
           \mathit{before}& =\mathrm{Performance\; scores \hspace{2pt} in \hspace{2pt}}\mathit{test}\\
           \mathrm{\bf if\;}\mathit{before} & >  \mathit{0}\\
           \mathrm{\bf then} &
           \left\{
            \begin{array}{l}
                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
                \mathrm{{\bf return}\;} R=\frac{\mathit{after}}{\mathit{before}}
            \end{array}
          \right.
   \end{array}\right.
\end{array} \right. 
\]}
 \caption{Experimental design .}\label{fig:design}
 \end{figure}

@@

Overall,  XTREE's plans were usually succinct--  in all our data sets,
 XTREE changes 
 usually changes around a fifth of the features (see \fig{types}.

@@

@@

Such a surprising plan can be  seen in the {\em lucene} results. Recall the standard advice for
OO systems: build classes that are internally cohesive with low coupling to other parts of the system~\cite{Dhama199565}. We can assess the relevance of this advice
to specific projects by checking how often a planner changes the
 coupling-related features:
\bi
\item {\em ca}:   afferent couplings  =  \# classes using this
				class;
\item {\em  	ce}:  efferent couplings =  \# classes  used by this
				  class. 
\item {\em cbm}: coupling between methods =  \# new/redefined methods
				to which all the inherited methods are coupled
\item	{\em cbo}:  coupling between objects = a value that increases when the methods of one
				class access services of another.

\item {\em ic}:   inheritance coupling =  \#parent classes  which a given
				class is coupled (includeing methods and variables inherited)
\ei
For the  {\em lucene} XTREE results  of  \fig{changed},
the most frequent change was to alter the lines of code in a class (see the tallest
red historgram in that figure on the {\em loc}, or lines of code). 
Looking at the logs of our planner, we can see
that XTREE's proposed changed is to {\em reduce} the size of a class.
The only way to do that,  while keeping the  same functionality, it is create a network
of smaller classes that interact to produce that functionality.
That is, we would need to {\em increase} the coupling of those classes to achieve XTREE's plan.

@@

In summary, XTREE satisfies that criteria that, sometimes, it produces surprising plans.
At least for the {\em lucene} data set, we can see advice that recommends {\em increasing coupling}
to reduce defects.

@@

% For example, the COCOMO model from University of 
% Southern California estimates software development time using a combination of industrial data and some domain expertise
% from its author (Barry Boehm). \fig{coc} shows results from using COCOMO 
% as an oracle to assess our planning methods. In this experiment, random projects were used as COCOMO
% inputs. This generated an development time estimate for each example, which we passed to our four methods.
% 40 times, we let those methods propose changes to those projects. 
% For assessment purposes, the changes projects were then feed back to the COCOMO
% oracle.

The POM3 model~\cite{boehm2003using},~\cite{port2008} is a tool for exploring that management challenge. POM3 implements the Boehm and Turner model of agile programming~\cite{boehm2003balancing} where teams select tasks as they appear in the scrum backlog.  POM3 can study the implications of different ways to adjust task lists in the face of shifting priorities. The model outputs estimates task completion rates; programmer idle rates; and total overall cost. POM3 represents requirements as a set of trees. POM3 models requirements as a dependency tree. A single requirement in the tree of a prioritization value and a cost, along with a list of child-requirements and dependencies. Before any requirement can be satisfied, its children and dependencies must first be satisfied. POM3 simulates changing priorities by making teams aware of random items in the requirements tree at random intervals, thus forcing teams to constantly readjust their "to do" lists. For further details on this model see~\cite{boehm2003balancing}, ~\cite{boehm2003using}, and ~\cite{port2008}. \fig{coc} shows results from using POM3 as an oracle to assess our planning methods and their ability to reduce the project cost. In this experiment, we generated a training and testing set with 1000 randomly generated instances, which we passed to our four methods.
40 times, we let those methods propose changes to those projects. 
For assessment purposes, the changes projects were then feed back to the POM3
oracle.

Using this approach, it is possible to assess the value of a plan by measuring its
effectiveness with respect to some ground truth (in this case, the POM3 model).
As shown in \fig{coc}, XTREE reduces the  passes this assessment. These results from the POM3 model further endorsed the conclusions of the rest
of this paper; i.e. compared to three other methods,  XTREE's supervised methods are best for generating plans on how to change example projects.

\subsection{  Feasibility}\label{sect:feasibility}
It is important to also explore the general practicality of the plans. To this end, we are currently undertaking a \textit{feasibility study} in collaboration with industrial partners to assess the general feasibility of our changes. With this study, we would like to understand the nature of changes suggested by XTREE. For example, we want to check if programmers are willing to implement the changes proposed by XTREE or are there other forces (e.g. social, psychological) that might block a team from accepting the advice of an outside oracle like XTREE. Note this a concern not just issues for XTREE, but for any tool proposing refactorings.

@@

Some organizations have the resources to 
run repeated trials to assess  project changes.
For example, in one   study, Bente et al. report results
were the same  specification that was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
to (say) take a code base, assign it to different teams, make these teams  adopt different polices,
then check in 12 months time
 which teams have fewer defects than the others.

@@

Four planners were assessed here for the tasks of reducing defects and runtimes. 
Three of the methods come from our prior publications~\cite{me12c,krishna15}, and the conclusion of this
paper is that a novel fourth method clearly out-performs the other three
(measured in terms of {\em effectiveness, succinctness, and surprise}).
We conjecture that XTREE worked better than the rest since:
\bi
\item
It uses a supervised method to divide the data and;
\item
When planning how to move examples to better classes, it is   best to  reflects over 
differences between those classes.
\ei

@@

As to scalability, XTREE is a post-processor to a decision tree algorithm. Hence, in theory,  XTREE   works on
  domain where data miners can generate decision trees. Given the current state of the art in Big Data,
can   XTREE  be applied to  very large data sets?

@@

\section*{Acknowledgements}
The work has partially funded by NSF  award \#1506586.
\bibliographystyle{plain}

### 2015-08-27 tex/results_models.tex
Updates from ShareLaTeX

\begin{figure}[!b]

@@

 ~\hrule~
\caption{Results: Methods 1,2,3,4 applied to some ground-truth data.
Values collected from   40 repeated runs of each method with different random seeds.
Results show ratios of (1) sum of development effort (in the changes examples) to (2)
the of the development effort in the original test data.
}\label{fig:coc}
\end{figure}

>>>>

\begin{figure}[!t]

@@

 ~\hrule~
\caption{Results: Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data.
}\label{fig:coc}
\end{figure}
